---
title: "Cytek Management 5/11/23"
#output: html_notebook
---

# Load Libraries

```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
library(chron)
```

# Read in data

Read in csv files for calendar and user/lab key

```{r Read in data}
cal_data <- read.csv('cytek_google_calendar.csv')
lab_key <- read.csv('lab_key.csv')
```

# Data wrangling

The dataframe needs a few preprocessing step:
  1.Separate date into month, day, and year.
  2.Coerce start and end column into time values.
  3.Create a use_time column by subtracting start time from end time
  4.Join lab_key to cal_data, adding a lab name column
  5.Remove NA values

```{r Data wrangling}
# Add :00 to all times for conversion
cal_data$start <- paste(cal_data$start, ':00')
cal_data$end <- paste(cal_data$end, ':00')

cal_data <- cal_data |>
  separate(date, into = c('month', 'day', 'year'), sep = '/' ) |>
  mutate(time_start = chron(times. = start),
         time_end = chron(times. = end),
         use_time = time_end - time_start) |>
  left_join(lab_key, by = c('name' = 'user')) |>
  na.omit()
```

As a final preprocessing step, this changes use_time from times class to numeric for easier plotting. The calender was taken as of 5/11, but it contains some future dated times for maitenance. I will remove the future times as they do not reflect current usage.

Also creating a single element variable `total_time` for later use.

```{r use_time numeric}
cal_data$use_time <- as.numeric(cal_data$use_time) * 24
total_time <- sum(cal_data$use_time)

cal_data <- cal_data[1:2665,]
```

# Plotting

Simple plot of total use time

```{r Total use_time plot}
ggplot(cal_data, aes(lab, use_time, fill = lab)) +
  geom_col()

ggsave('total_use_plot.png',
       last_plot(),
       width = 6,
       height = 4,
       units = 'in',
       dpi = 300)
```

Create a new dataframe that groups by lab. Summarize and create a variable of total use time by lab called `lab_use`. Divide `lab_use` by total time to get a percentage named `total_use`. Create `time_label` which formats `total_use` to few decimals for later use as a graph label.

```{r cal_data group by lab}
by_lab <- cal_data |>
  group_by(lab) |>
  summarize(lab_use = sum(use_time)) |>
  mutate(total_use = lab_use / total_time * 100,
         time_label = format(round(total_use, 1), nsmall = 1))

```

Create the total use plot again, this time using percentages and displaying the percentages.

```{r Total use_time plot with percentages}
ggplot(by_lab, aes(lab, total_use, fill = lab)) +
  geom_col() +
  geom_text(aes(label = time_label), vjust = -0.3)

ggsave('total_use_perc_plot.png',
       last_plot(),
       width = 6,
       height = 4,
       units = 'in',
       dpi = 300)
```




