---
title: "Cytek Management"
#output: html_notebook
---

# Load Libraries

```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
library(chron)
```

# Read in data

Read in csv files for galender and user/lab key

```{r}
cal_data <- read.csv('cytek_google_calendar.csv')
lab_key <- read.csv('lab_key.csv')
```

# Data wrangling

First I need to tidy this data by separating the date into individual columns.

add :00 to times
convert times into new column
create use time column
remove NA values
 

```{r}
# Add :00 to all times for conversion
cal_data$start <- paste(cal_data$start, ':00')
cal_data$end <- paste(cal_data$end, ':00')

cal_data <- cal_data |>
  separate(date, into = c('month', 'day', 'year'), sep = '/' ) |>
  mutate(time_start = chron(times. = start),
         time_end = chron(times. = end),
         use_time = time_end - time_start) |>
  na.omit() 
```


Since the `name` column contains values entered by all the users, it is a mix of upper and lower case as well


# In progess code


```{r temp variables}
temp <- data.frame(name = unique(cal_data$name)) # make a new df of unique name values
```

```{r}
pattern_replacements <- c("Ashley" = "Ashley",
                          'Jess' = 'Jessica',
                          'Alex' = 'Alex',
                          'Laura' = 'Laura',
                          'Eric' = 'Eric',
                          'Dejene' = 'Dejene',
                          'DT' = 'Dejene',
                          'Dallas' = 'Dallas',
                          'Elena' = 'Elena',
                          'Joe' = 'Joe',
                          'Amandip' = 'Amandip',
                          'Spencer' = 'Spencer',
                          'Sunny' = 'Sunny',
                          'Therese' = 'Therese',
                          'ri' = 'Ritz',
                          'we' = 'Wenjuan',
                          'Kiana' = 'Kiana',
                          'Clarissa' = 'Clarissa',
                          'Regan' = 'Regan',
                          'Craig' = 'Craig',
                          'Rachel' = 'Rachel',
                          'Kristen' = 'Kristen',
                          'Joselyn' = 'Joselyn',
                          'Cytek' = 'Cytek',
                          'qc' = 'Cytek',
                          'warmup' = 'Cytek'
                          )
```

```{r}
patt <- c("Ashley", 'Jess', 'Alex', 'Laura', 'Eric', 'Dejene', 'DT', 'Dallas', 'Elena', 'Joe', 'Amandip', 'Spencer', 'Sunny', 'Therese', 'ri', 'we', 'Kiana', 'Clarissa', 'Regan', 'Craig', 'Rachel', 'Kristen', 'Joselyn' , 'Cytek', 'qc', 'warmup')

rep <- c("Ashley", 'Jessica', 'Alex', 'Laura', 'Eric', 'Dejene', 'Dejene', 'Dallas', 'Elena', 'Joe', 'Amandip', 'Spencer', 'Sunny', 'Therese', 'Ritz', 'Wenjuan', 'Kiana', 'Clarissa', 'Regan', 'Craig', 'Rachel', 'Kristen', 'Joselyn', 'Cytek', 'Cytek', 'Cytek')
```



```{r}
temp$name <- gsub(pattern = paste(names(pattern_replacements), collapse = "|" ),
                  replacement = pattern_replacements,
                  x = temp$name,
                  ignore.case = T)

temp$name <- str_replace_all(temp$name, regex(patt, ignore_case = T), rep)
```



```{r}
rm(name.cleaner)
```





```{r}
temp_2 <- data.frame(var1 = unique(temp$name))
```






# Save below

```{r}
#### THIS WORKS!!! 
temp_2 <- temp |>
  mutate(clean_names = ifelse(grepl('ri', name, ignore.case = T), 'Ritz', name))
```

# Function set up testing

I think I can use a function to iterate through the names rather than list them one by one. Below are code chunk notes for that

```{r make name_df}
name_df <- data.frame(pattern = c('ri', 'we'),
                      cleaned = c('Ritz', 'Wenjuan'))
```


```{r function set up}
name.cleaner <- function(x, y, z) {
  for (i in x) {
    mutate(z, clean_names = ifelse(grepl(x, y, ignore.case = T), y, name))
  }
}
```


